\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.5cm, top=1.2cm, bottom=1cm]{geometry}
\usepackage{charter} % Serif font similar to the reference
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{array}
\usepackage{setspace}

% Colors
\definecolor{linkcolor}{HTML}{000000}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
}

% Remove page numbers
\pagenumbering{gobble}

% Custom section command matching the reference style
% Line ABOVE the section name, section name on left margin
\newcommand{\cvsection}[1]{%
    \vspace{0.8em}
    \noindent
    \begin{minipage}[t]{2.5cm}
        \rule{2cm}{0.4pt}\\[0.2em]
        {\large #1}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{13.5cm}
        \vspace{1.4em}
    \end{minipage}
    \vspace{0.1em}
}

% Entry with date, title, subtitle, and description
\newcommand{\cventry}[4]{%
    \noindent
    \begin{minipage}[t]{2.5cm}
        \raggedleft
        \small #1
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{13.5cm}
        \textbf{#2}\\
        \textit{#3}\\[0.2em]
        #4
    \end{minipage}
    \vspace{0.5em}
}

% Entry without description (for education, simple items)
\newcommand{\cventrysimple}[3]{%
    \noindent
    \begin{minipage}[t]{2.5cm}
        \raggedleft
        \small #1
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{13.5cm}
        \textbf{#2}\\
        #3
    \end{minipage}
    \vspace{0.4em}
}

% Single line entry (for awards, languages)
\newcommand{\cvline}[2]{%
    \noindent
    \begin{minipage}[t]{2.5cm}
        \raggedleft
        \small #1
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{13.5cm}
        #2
    \end{minipage}
    \vspace{0.2em}
}

\begin{document}

% Header
\noindent
\begin{minipage}[t]{0.55\textwidth}
    {\fontsize{34}{40}\selectfont\textbf{Victor Maricato}}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.42\textwidth}
    \raggedleft
    \small
    \href{mailto:maricatovictor@gmail.com}{maricatovictor@gmail.com}\\
    \href{https://linkedin.com/in/victormaricato}{\underline{LinkedIn}} · \href{https://github.com/victormaricato}{\underline{GitHub}}
\end{minipage}

% Employment
\cvsection{Employment}

\cventry{09/2022 -- 01/2026}{Upwork}{Staff Machine Learning Engineer · San Francisco (Remote)\newline \textnormal{Senior Machine Learning Engineer (01/2024 -- 04/2025)}\newline \textnormal{Machine Learning Engineer (09/2022 -- 01/2024)}}{Led team of 3 on LLM and information retrieval research. Drove >\$60M revenue impact using Small Language Models with <200ms latency. Led development of internal RAG model for chat and proposal generation (\href{https://www.upwork.com/uma}{\underline{Upwork Uma}}). Published at EMNLP 2025: \href{https://aclanthology.org/2025.emnlp-industry.154/}{\underline{DispatchQA}}.}

\cventry{09/2020 -- 09/2022}{Mendelics}{Data Scientist · São Paulo}{Built variant prediction model used in Brazil's public healthcare system. Reduced medical revision by 90\%+. Deployed SARS-CoV-2 pipeline; contributed to PANGOLIN.}

\cventry{04/2019 -- 08/2020}{OLX}{Data Scientist Intern · Rio de Janeiro}{Churn prediction, image-based category suggestions, Bayesian analysis for ad optimization.}

\cventry{12/2017 -- 04/2019}{Shell}{Research Engineer (Biotechnology) · Rio de Janeiro}{Increased bioproduct yield by 27.4\% through Deep Learning regression models.}

% Projects
\cvsection{Projects}

\cventry{2026}{\href{https://focusy.co}{\underline{Focusy.co}}}{Founder · Stockholm}{Reading assistant that parses content from documents, images, and web pages into RSVP format to help users read faster and understand content better.}

\cventry{2024 -- 2025}{\href{https://kannel.ai}{\underline{Kannel.AI}}}{Founder · Stockholm}{Speech-to-text models with prompt-guided and formatted transcription.}

% Education
\cvsection{Education}

\cventrysimple{2024 -- 2025}{MSc Medical Science · MSc Science}{Karolinska Institute · Stockholm University}

\cventrysimple{2019 -- 2023}{BSc Information Systems}{Federal University of Rio de Janeiro}

\cventrysimple{2020 -- 2021}{Visiting Student in Computer Science (AI)}{Heriot-Watt University, Edinburgh}

\cventrysimple{2014 -- 2018}{Technical Degree in Biotechnology}{Federal Institute of Rio de Janeiro}

% Additional
\cvsection{Additional}

\cvline{2022 -- 2023}{\textbf{Research Assistant} · MIT CSAIL (Part-time)}

\cvline{2022}{\textbf{Google's Advanced Solutions Lab: Machine Learning}}

\cvline{Languages}{English (Fluent, TOEFL 102) · German (Intermediate) · Portuguese (Native)}

% Publications
\cvsection{Publications}

\cvline{}{See \href{https://scholar.google.com/citations?user=WaAoUqsAAAAJ}{\underline{Google Scholar}}}

\end{document}
